\documentclass[ComputerScience,10pt]{vita}
\usepackage{fullpage}
\usepackage{times}
\usepackage{url}

\newcommand{\comment}[1]{}

\begin{document}
\name{{Alex David Groce}}
%\businessAddress{School of Electrical Engineering and Computer Science\\ Oregon State University\\ 1148 Kelley Engineering Center\\ Corvallis, OR 97331-5501} 
%  \homeAddress {US Citizen}


\newcategory{Teaching}
\newcategory{Current Students}
\newcategory{Graduated Students}
\newcategory{Research Interests}
\newcategory{Selected Presentations}
\newkind{Topics}
\newcategory{Education}
\newcategory{Professional Activities and Service}
\newcategory{Books, Edited Volumes}
\newcategory{Selected Recent Conference Publications}
%\newcategory{Refereed Conference Tool Publications}
%\newcategory{Refereed Workshop Publications}
\newcategory{Selected Recent Journal Publications}
\newcategory{Technical Reports}
\newcategory{Columns, Book Reviews, and Magazine Articles}
\newcategory{Invited Seminars}
\newcategory{Invited Talks and Panels}
\newcategory{Invited Papers}
\newcategory{Panel and Committee Service}
\newcategory{Funding}
\newkind{Expected}

\begin{vita}

%\begin{Expected Degrees}
%\end{Expected Degrees}

\vspace{-0.4in}

\begin{Education}
  \item Ph.D., {\bf Computer Science}, Carnegie Mellon University, March 2005
  \item B.S., {\bf Computer Science, Multidisciplinary Studies}, North Carolina State University, May 1999 (\emph{summa cum laude})
\end{Education}

\begin{Experience}
\item {\bf Summary:} My
  work focuses on testing, developing, specifying, and understanding
  critical distributed, embedded, aerospace, systems, and security
  software and software/hardware systems.  I have been PI or co-PI on externally funded grants
  totalling over \$9.1M (\$1.2M my share), and have authored or
  co-authored more than 60 publications, primarily in ACM, IEEE, and
  top verification and formal methods venues, with over 3,100 citations,
  an h-index of 29, and an i10-index of 50, according to Google
  Scholar.

\item {\bf 1/2017--present $\cdot$ Associate Professor with Tenure, Northern Arizona University}

  \item {\bf 9/2015--12/2016 $\cdot$ Associate Professor with Tenure, Oregon State University}

  \item {\bf 6/2009--9/2015 $\cdot$ Assistant Professor, Oregon State
    University}

  \item {\bf 4/2005--6/2009 $\cdot$ Laboratory for Reliable Software,
    NASA Jet Propulsion Laboratory:} Led test automation development and
    design, Mars Science Laboratory (Curiosity rover) Flight Software
    Internal Test Team.  
\end{Experience}


\begin{Honors}
\item ACM/IEEE International Conference on Software Engineering 2016 {\bf Distinguished Poster Award}
  \item IEEE International Conference on Software Testing, Verification and Validation (ICST) 2014 {\bf Best Paper Award}
  \item National Science Foundation Faculty {\bf Early Career Development (CAREER) Program Award}, 2011
  \item {\bf JPL Mariner Award} for LogScope Testing Software, 2009
  \item {\bf JPL Spot Award} (for Multi Mission System Architecture Platform
  (MSAP) File System Testing), 2006 \item ACM/IEEE International Conference on Software Engineering 2003 {\bf ACM SIGSOFT
  Distinguished Paper Award} 
\end{Honors}


\begin{Funding}
\item ``Interfaces, Models, and Monitoring for Resource-aware
  Transformations that Augment the Lifecycle of Systems (IMMoRTALS)'',
  Co-PI, DARPA BRASS (Building Resource Adaptive Software Systems), BAA-15-36, \$464,625, \$1.6M total Oregon State University budget, (total project budget \$7.7M), October 2015-September 2019.
\item ``Advanced Tools for Effective Automated Test Generation'', PI, \emph{NASA Small Business Technology Transfer Phase I} T11.01-9878, \$52,037 (total budget \$125,000), July 2015-2016.
\item ``Explorations of Testing in the Cloud'', PI, Amazon Web Services in Education Grants, \$10,000, January 2015-2017.
\item ``II-EN: Software Tools for Monte-Carlo Optimization'', Co-PI, \emph{National Science Foundation} CNS-1406049, \$442,366, October 2014-September 2017 (infrastructure development for cloud-based optimization tools with ML, graphics, and testing applications; includes \$12,000 dedicated compute time for software testing research).
\item ``Diversity and Feedback in Random Testing for Systems
  Software'', PI, \emph{National Science Foundation} CCF-1217824, \$242,244 (total budget \$491,280), September 2012-2015.
\item ``CAREER: Integrating Automated Software Testing Methods'', PI, \emph{National Science Foundation} CCF-1054876, \$400,000, September 2011-2016.
\end{Funding}


\begin{Selected Recent Journal Publications}
\item
Rahul Gopinath, Iftekhar Ahmed, Mohammad Amin Alipour, Carlos Jensen, and {\bf Alex Groce}.
\newblock Does Choice of Mutation Tool Matter?
\newblock \emph{Software Quality Journal}, 25(3):871-920, September 2017.

\item
{\bf Alex Groce}, Mohammad Amin Alipour, Chaoqiang Zhang, Yang Chen, and John Regehr.
\newblock Cause Reduction: Delta Debugging, Even Without Bugs.
\newblock \emph{Software Testing, Verification and Reliability}, 26(1):40-68, January 2016.

\item
Milos Gligoric, {\bf Alex Groce}, Chaoqiang Zhang, Rohan Sharma, Mohammad Amin Alipour, and Darko Marinov.
\newblock Guidelines for Coverage-Based Comparisons of Non-Adequate Test Suites.
\newblock \emph{ACM Transactions on Software Engineering and Methodology}, 24(4):4-37, August 2015.

\item
{\bf Alex Groce}, Todd Kulesza, Chaoqiang Zhang, Shalini Shamasunder, Margaret Burnett, Weng-Keen Wong, Simone Stumpf, Sh
ubhomoy Das, Amber Shinsel, Forrest Bice, and Kevin McIntosh.
\newblock You Are the Only Possible Oracle: Effective Test Selection for End Users of Interactive Machine Learning Systems.
\newblock \emph{IEEE Transactions on Software Engineering}, 40(3):307-323, March 2014.
\end{Selected Recent Journal Publications}

\begin{Selected Recent Conference Publications}
\item Arpit Christi, {\bf Alex Groce}, and Rahul Gopinath.
\newblock Resource Adaptation via Test-Based Software Minimization.
\newblock \emph{IEEE International Conference on Self-Adaptive and Self-Organizing Systems}, accepted for publication, Tucson, Arizona, September 2017 (acceptance rate 21\%).

\item {\bf Alex Groce}, Josie Holmes, and Kevin Kellar.
\newblock One Test to Rule Them All.
\newblock \emph{ACM International Symposium on Software Testing and Analysis}, pp. 1-11, Santa Barbara, California, July 2017 (acceptance rate 26\%).

\item Rahul Gopinath, Carlos Jensen, and {\bf Alex Groce}.
\newblock The Theory of Composite Faults.
\newblock \emph{IEEE International Conference on Software Testing, Verification and Validation}, pp. 47-57, Tokyo, Japan, March 2017 (acceptance rate 27\%).

\item Iftekhar Ahmed, Rahul Gopinath, Caius Brindescu, {\bf Alex Groce}, and Carlos Jensen.
\newblock Can Testedness be Effectively Measured?
\newblock \emph{ACM SIGSOFT International Symposium on the Foundations of Software Engineering},  pp. 547-558, Seattle, Washington, November 2016 (acceptance rate 27\%).

\item Mohammad Amin Alipour, August Shi, Rahul Gopinath, Darko Marinov, and {\bf Alex Groce}.
\newblock Evaluating Non-Adequate Test-Case Reduction.
\newblock \emph{IEEE/ACM International Conference on Automated Software Engineering}, pp. 16-26, Singapore, Singapore, September 2016 (acceptance rate 20\%).

\item Rahul Gopinath, Amin Alipour, Iftekhar Ahmed, Carlos Jensen, and {\bf Alex Groce}.
\newblock On the Limits of Mutation Reduction Strategies.
\newblock \emph{International Conference on Software Engineering}, pp. 511-522, Austin, Texas, May 2016 (acceptance rate 19\%).

\item
Chaoqiang Zhang, {\bf Alex Groce}, and Mohammad Amin Alipour.
\newblock Using Test Case Reduction and Prioritization to Improve Symbolic Execution.
\newblock \emph{ACM International Symposium on Software Testing and Analysis}, pp. 60-70, San Jose, California, July 2014 (acceptance rate 28\%).

\item
Rahul Gopinath, Carlos Jensen, and {\bf Alex Groce}.
\newblock Code Coverage for Suite Evaluation by Developers.
\newblock \emph{International Conference on Software Engineering}, pp. 72-82, Hyderabad, India, May-June 2014 (acceptance rate 20\%). 

\item
{\bf Alex Groce}, Mohammad Amin Alipour, Chaoqiang Zhang, Yang Chen, and John Regehr.
\newblock Cause Reduction for Quick Testing.
\newblock \emph {IEEE International Conference on Software Testing, Verification and Validation}, pp. 243-252, Cleveland, Ohio, March-April 2014 (acceptance rate 28\%), {\bf Best Paper Award}.

\item Yang Chen, {\bf Alex Groce}, Chaoqiang Zhang, Weng-Keen Wong, Xiaoli Fern, Eric Eide, and John Regehr.
\newblock Taming Compiler Fuzzers.
\newblock \emph{ACM SIGPLAN Conference on Programming Language Design and Implementation}, pp. 197-208, Seattle, Washington, June 2013 (acceptance rate 17\%).


\end{Selected Recent Conference Publications}


\end{vita}
\end{document}
